Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-14 report/report.tex
Update scientific study disposition

The same methods can be applied to import building footprint data from OSM or some, and the same metrics can be applied to assess the data accuracy.
When we have the fundamental
we can proceed with building modeling (Parish Müller, procedural building modeling). Other challenges include infering or guessing building height. () have presented a method for inferring building height from the building footprint alone, with surprising accuracy.

>>>>

The same methods can be applied to import building footprint data from OSM or some, and the same metrics can be applied to assess the data accuracy. (Fan et al)
When we have the fundamental procedure for accuratly importing building footprints without compromising the data integritey, we can proceed with building modeling (Parish Müller, procedural building modeling). Other challenges include infering or guessing building height. () have presented a method for inferring building height from the building footprint alone, with surprising accuracy.

Depending on the level of data we have access to, we can then choose what level of representation we would like for our application (Todor).
We may also chose what LOD class(es) to use depending on data availablity and application. (find reference)
